02_limma_hyp_grouped

### 2019-04-03 analysis/02_limma_hyp_grouped.Rmd
remove volcano
now with all the plots

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         femaleBL = femalebldg - femalelay,
	         femaleLI = femalelay - femaleinc,
	         femaleIH = femaleinc - femalehatch,
	         femaleHN = femalehatch -  femalenestl,
	         femaleBL = femalebldg - femaleinc,
	         femaleBL = femalebldg - femalehatch,
	         femaleBL = femalebldg - femalenestl,
	         femaleLH = femalelay - femalehatch,
	         femaleLN = femalelay - femalenestl,
	         femaleHN = femalehatch - femalenestl,

	         maleBL = malebldg - malelay,
	         maleLI = malelay - maleinc,
	         maleIH = maleinc - malehatch,
	         maleHN = malehatch -  malenestl,
	         maleBL = malebldg - maleinc,
	         maleBL = malebldg - malehatch,
	         maleBL = malebldg - malenestl,
	         maleLH = malelay - malehatch,
	         maleLN = malelay - malenestl,
	         maleHN = malehatch - malenestl,

@@

```{r volcanoplots}
for(i in mycontrasts){
  plotVolcanos(i) 
}
```

>>>>

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         femaleBL = femalebldg - femalelay,
	         femaleLI = femalelay - femaleinc,
	         femaleIH = femaleinc - femalehatch,
	         femaleHN = femalehatch -  femalenestl,
	         femaleBI = femalebldg - femaleinc,
	         femaleBH = femalebldg - femalehatch,
	         femaleBN = femalebldg - femalenestl,
	         femaleLH = femalelay - femalehatch,
	         femaleLN = femalelay - femalenestl,
	         femaleHN = femalehatch - femalenestl,

	         maleBL = malebldg - malelay,
	         maleLI = malelay - maleinc,
	         maleIH = maleinc - malehatch,
	         maleHN = malehatch -  malenestl,
	         maleBI = malebldg - maleinc,
	         maleBH = malebldg - malehatch,
	         maleBN = malebldg - malenestl,
	         maleLH = malelay - malehatch,
	         maleLN = malelay - malenestl,
	         maleHN = malehatch - malenestl,

@@
